%sri
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{As Much Resilience As You Want: \\Application-tailored Resilience in Legion}

%\author{\IEEEauthorblockN{Karthik Murthy} \and
%\IEEEauthorblockN{Mike Bauer} \and 
%\IEEEauthorblockN{Manolis Papadakis} \and
%\IEEEauthorblockN{Kyushick Lee} \and
%\IEEEauthorblockN{Yongkee Kwon} \and
%\IEEEauthorblockN{Wonchan Lee} \and
%\IEEEauthorblockN{Todd Warszawski} \and 
%\IEEEauthorblockN{Elliott Slaughter} \and
%\IEEEauthorblockN{Sean Treichler} \and
%\IEEEauthorblockN{Alex Aiken} \and
%\IEEEauthorblockN{Mattan Erez}
%}

\maketitle

\begin{abstract}
Resilient is an important aspect of scaling applications on
large clusters. As we approach parallelism profiles of several millions and long running applications, we need to ensure that ineffect ``we reach the end".
Defining the policy interaction with the programming model features necessitates that we revisit the memory concistency model. 
Recoverability, a critical step in
resilience, opens the door to optimizations such as speculation. We also
evaluate this.  \dots
\end{abstract}

\begin{IEEEkeywords}
resilience, legion
\end{IEEEkeywords}

\input{introduction}

\input{resilience_overview}

\input{resilience_policy_with_legion_features}

\input{resilience_implementation}

\input{speculation}

\input{experiments}

\input{extensions}

\input{related_work}

\section{Conclusion}

\section*{Acknowledgment}

\begin{thebibliography}{00}
\bibitem{legion} S. Treichler, M. Bauer, and A. Aiken. Language support for
dynamic, hierarchical data partitioning. In Object Oriented Programming,
Systems, Languages, and Applications (OOPSLA), 2013.

\bibitem{x10}D. Grove et al. Failure Recovery in Resilient X10. IBM Research
Report, RC25660 (WAT1707-028) July 21, 2017.

\bibitem{schroeder_gibson}B. Schroeder and G. Gibson. Disk failures in
the real world: What does an MTTF of 1,000,000 hours mean to you. In 
Proceedings of the 5th USENIX conference on file and storage technologies
(FAST), pp. 1–16, 2007.

\bibitem{charm++}Acun et al. Power, Reliability, and Performance: One System to Rule them All
In Computer Issue No. 10 - Oct. 2016 vol. 49. ISSN: 0018-9162. pp: 30-37.

\bibitem{parsec} C. Cao, G. Bosilca, T. Herault, and J. Dongarra. Design for a
soft error resilient dynamic task-based runtime. In 29th IEEE International
Parallel \& Distributed Processing Symposium (IPDPS), May 2015.

\bibitem{errors_ecc}A. Geist, “What is the monster in the closet?” Invited Talk
at Workshop on Architectures I: Exascale and Beyond: Gaps in Research, Gaps in
our Thinking, aug 2011.

\bibitem{snir}M. Snir et al. Addressing failures in exascale computing. In The
International Journal of High Performance Computing Applications 2014, Vol.
28(2) 129–173.

\end{thebibliography}

\end{document}
